---
title: "Delaware Workforce Developement Board - BDM"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE) 
```

```{r read data, message=FALSE}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  # add required libraries here
  plotly,
  ggplot2,
  readxl,
  tidyverse,
  cluster,
  factoextra,
  tibble,
  scales,
  purrr)


# get the all necessary files
variable_value <- read_excel("value2.xlsx")
variable_info <- read_excel("Delaware BDM Final 2022 MAP variable info.xlsx")
variable_info[81,2] <-  "Other"  # Replace: Other (Specify)
variable_info[78,2] <-  "Word of mouth"
variable_info[198,2] <-  "Other"  # Replace: Other (Specify)
variable_info[219,2] <-  "Other"  # Replace: Other (Specify)
variable_info[248,2] <-  "Other"  # Replace: Other (Specify)
variable_info[269,2] <-  "Other"  # Replace: Other (Specify)
  
labels <- "industries_organized.csv" %>%
  read_csv() %>%
  select(index:naics) %>%
  dplyr::rename(Industry=index) %>%
  mutate(Industry=as.factor(Industry))

BDM_Final_Data <- read_excel("Delaware BDM Final 2022 DATA ADDED ZIPS.xlsx")
#BDM_Final_Data_Words<- read_excel("Delaware BDM Final 2022 DATA WORDS ADDED ZIPS.xlsx")

```

```{r clean data}
#clean "Yes"=1, "No"=0 entries. 
variable_value[variable_value == "0(1)"] <- "0"

#convert float to integer
variable_value$Sample_Number <- as.integer(variable_value$Sample_Number)

industries <- variable_value$Label[40:59]

# Create a copy of the dataset
BDM_Final_Copy <- BDM_Final_Data

#convert to numeric values
BDM_Final_Copy[] <- lapply(BDM_Final_Copy, function(x) {
    if(is.factor(x)) as.numeric(as.character(x)) else x
})
# sapply(BDM_Final_Copy, class)

#keep sample number seperate
#SAM_NO = BDM_Final_Copy["SAM_NO"]
BDM_Final_Clean <- BDM_Final_Copy

lbl <- c("Agriculture","Mining","Construction","Manufacturing","Wholesale","Retail","Transportation",
         "Utilities", "Information","Finance","Real Estate","Professional","Management","Administrative",
         "Educational", "Health Care","Arts","Accommodation","Other Services","Unsure") 

growth_industries <- data.frame("Industry"= c(1,3,4,10,12,15,16),
                                "names" = c("Food and Agriculture",
                                            "Construction and Mechanical Trades ",
                                            "Manufacturing, Logistics and Transportation",
                                            "Financial and Business Services",
                                            "Science and Technology",
                                            "Education",
                                            "Health Care"
                                )
)
```




## Number of Employees Within the Company {.tabset}

### Company Size Distributions
```{r S3 bar graph, fig.width=8, fig.height=6, fig.align='center'}
set.seed(123)
S3_plot_data <- dplyr::count(BDM_Final_Clean,S3) %>% 
  dplyr::rename(Count=n) %>% 
  mutate(Percentage=percent(round(Count/sum(Count),3))) %>% 
  mutate(labels = paste0(Percentage," (",Count,")")) %>% 
  mutate(prop = Count/sum(Count)) %>% 
  mutate(ypos = 360*(cumsum(prop)-0.5*prop)) %>% 
  mutate(yang = 90 + ypos)

S3_data <- data_frame(S3 = 1:10, 
                      Variable = c("1/Sole proprietorship","2-10","11-25","26-50","51-75","76-100","101-499","500-1000","1000+","Refuse"))

S3_data$Variable <- factor(S3_data$Variable,
                                levels=c("2-10","11-25","26-50","51-75","76-100","101-499","500-1000","1000+"))


S3_plot_data <- dplyr::inner_join(S3_data,S3_plot_data, by="S3")

ggplotly(
  S3_plot_data %>% 
ggplot(aes(x= Variable,
          y=Count,
        text=paste(
         "<br><b>&#8226; Count: </b>",Count,
         "<br><b> &#8226; Percent: </b>",Percentage
       ), group=1)) +
  theme(axis.text.x = element_text(angle = 90),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  geom_bar( stat = "identity", position = "stack",color="#d95f0e",fill="#fec44f") +
  ggtitle("What is the Number of Employees in Your Company?") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Number of Employees Within the Company") +
  ylab("Response of the Business (Count)") +
  scale_fill_brewer(palette="Set1") +
  theme_classic(),tooltip = c("text")
)


```

 + 75% of the included business staff 100 or less persons in Delaware.

```{r S3 pie chart, include=FALSE}
### Pie chart of company size 
# S3_plot_data$Variable <- factor(S3_plot_data$Variable, levels = rev(as.character(S3_plot_data$Variable)))
S3_plot_data$Variable <- factor(S3_plot_data$Variable,
                                levels=c("2-10","11-25","26-50","51-75","76-100","101-499","500-1000","1000+"))
ggplot(S3_plot_data,aes(x= "",y=Count, fill=Variable)) +
  geom_bar(width = 1, stat = "identity", color="white", alpha=0.9) +
  coord_polar("y",start = 0) +
  ggtitle("What is the Number of Employees in Your Company?") +
  #geom_text(aes(label=labels, angle=c(0,0,0,65,80,0,45,0)),position=position_stack(vjust=0.5), size=3, color="black") +
  geom_text(aes(label=labels, angle=c(0,0,0,305,325,0,30,0)),position=position_stack(vjust=0.5), size=3, color="black") +
  #geom_text(aes(label=labels, angle=yang),position=position_stack(vjust=0.5), size=3, color="black") +
  theme_void() +
  scale_fill_brewer(palette="Set1") + 
  guides(fill = guide_legend(title = "Company Size"))

```


### Company size distributions across industries
```{r D4A Industries with S3, fig.width=10, fig.height=6, fig.align='center'}
S3_data <- data_frame(S3 = 1:10, 
                      Variable = c("1/Sole proprietorship","2-10","11-25","26-50","51-75","76-100","101-499","500-1000","1000+","Refuse"))
  
D4A_plot_data <- BDM_Final_Clean %>% 
  dplyr::count(D4A,S3,name="Count") %>% 
  dplyr::inner_join(S3_data,D4A_plot_data, by="S3") %>% 
  dplyr::rename(Industry=D4A) %>% 
  dplyr::mutate(Industry = as.factor(Industry)) %>% 
  dplyr::inner_join(labels,D4A_plot_data, by="Industry") %>% 
  dplyr::rename(Size=Variable) %>% 
  group_by(Size) %>% 
  dplyr::mutate(Percentage =round(Count/sum(Count),3)) %>% 
  ungroup() %>% 
  rename(industry=Industry, Industry=names)
# %>% 
#    head() %>%
#    dput()

D4A_plot_data1 <- D4A_plot_data %>%
  mutate(under_100 = case_when(
    Size %in% c("2-10", "11-25", "26-50", "51-75", "76-100") ~ "100 and below",
    Size %in% c("101-499","500-1000","1000+") ~ "Above 100")
  ) %>%
  group_by(Industry, under_100) %>% 
  summarise(Total = sum(Count)) %>% 
  ungroup() %>% 
  group_by(Industry) %>% 
  mutate(Percentage = round(Total/sum(Total),3)) %>%  
  ungroup() %>% 
  mutate(Industry = fct_reorder(Industry, Percentage))

```

```{r D4A ggplotly graph, fig.width=10, fig.height=6, fig.align='center'}
ggplotly(
  D4A_plot_data1 %>%
    mutate(Percent_yes = if_else(under_100=="100 and below",Percentage,NA_real_)) %>%
    fill(Percent_yes) %>%
    mutate(Industry=fct_reorder(Industry, Percent_yes)) %>% 
    ggplot(aes(x= Percentage,
               y=Industry,
               fill=under_100,
               text=paste(
                 "<b>&#8226; Growth industry: </b>",Industry,
                 "<br><b> &#8226; Response within industry: </b>",100*Percentage,"%",
                 "<br><b> &#x2022; Total within industry: </b>",Total),
               group=Industry
    )) +
    geom_col( position = "stack") +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_brewer(palette = "Set2") + 
    labs(title = "Company Size Across Industries", 
         x = "Company Size (Percentage)" , 
         y = "") +
    guides(fill = guide_legend(title = "Company size")) +
    theme_classic() +
    theme(axis.text.x = element_text(angle  = 0, size = 8),
          plot.title = element_text(size = 11, face = "bold"),
          axis.title.y = element_text(size = 11)),
  tooltip = c("text")
)%>% layout(hoverlabel = list(align = "left")) 
```

```{r D4A plot using plotly,fig.width=10, fig.height=7,include=FALSE}
library(plotly)
D4A_plot_data$Size <- factor(D4A_plot_data$Size,
                          levels=c("2-10","11-25","26-50","51-75","76-100","101-499","500-1000","1000+"))
fig <- plot_ly(
  data = D4A_plot_data,
  x = ~Size,
  y = ~Count,
  color = ~Industry,
  type = "bar",
  #orientation = 'h',
  text = ~Industry,
  hovertemplate = ~paste(
    '</br><b> %{text}</b><br>',
    '</br> <b>Count:</b>',Count,
    '</br> <b>Within company size:</b>',Percentage,'%')
)
fig <- fig %>% 
  layout(barmode = "stack",
         title = list(text = '<b> Company Size Across Primary Industries </b>'),
         xaxis = list(title = list(text='<b> Number of Employees Within the Company</b>')),
         yaxis = list(title = list(text='<b> Response of the Business (Count) </b>')),
         legend = list(title = list(text = '<b> Company Size</b>')),
         xaxis = list(categoryorder = "total descending")
  )
fig

```














## Growth within industries {.tabset}

### Staff Working Remotely
```{r Q3 plot over time fro each industry-b, fig.width=10, fig.height=6, fig.align='center'}
library(dplyr)
library(ggplot2)

Q3_line_data <- aggregate(Q3A~D4A, BDM_Final_Clean,mean)
Q3_line_data <- cbind(Q3_line_data,aggregate(Q3B~D4A, BDM_Final_Clean,mean)[2])
Q3_line_data <- cbind(Q3_line_data,aggregate(Q3C~D4A, BDM_Final_Clean,mean)[2])

Q3_line_data <- Q3_line_data %>% 
  mutate(Industry = as.factor(D4A)) %>% 
  dplyr::rename(`Current` = Q3A, `6 Months` = Q3B, `12 Months` = Q3C) %>% 
  pivot_longer(Current:`12 Months`, names_to = "time") %>% 
  mutate(time=as.factor(time)) %>% 
  mutate(time = fct_relevel(time, c("Current","6 Months","12 Months")))

merged <- inner_join(labels,Q3_line_data, by="Industry") %>% 
  dplyr::rename(industry=Industry, Industry=names)
  
  
  # mutate(absolute_change = Size %in% c("2-10", "11-25", "26-50", "51-75", "76-100")) %>% 
  # group_by(Industry) %>% 
  # mutate(company_count = )
  # mutate(percent = company_count / sum(company_count)) %>% 
  # ungroup() %>% 
  # mutate(percent_under_100 = if_else(under_100, percent, NA_real_)) %>%
  # fill(percent_under_100) %>%
  # mutate(Industry = fct_reorder(Industry, percent_under_100))
  # 
  

ggplotly( 
  merged %>% 
  ggplot(aes(x=time, y=value, color=Industry, group=Industry)) + 
  geom_point() +
  geom_line() +
  ggtitle("Percentage of Staff Working Remotely Over Time Across Industries") +
  xlab("Time Frame (months)") +
  ylab("Percent of Staff") +
  theme_bw() #) %>% 
  #layout(legend = list(orientation = "h")
  )

```


### Positions to Fill
```{r Q28 longitudinal analysis by indistry - data prepare 1}
Q28_plot_data <- dplyr::count(BDM_Final_Clean,Q28C) %>% 
  dplyr::rename(Count=n) %>% 
  dplyr::mutate(total = sum(Count))

data <- BDM_Final_Clean %>% select("D4A","Q28A","Q28B","Q28C")
Q28_data <- subset(data, Q28C!= 8)
Q28_data <- subset(Q28_data, Q28B!= 8)
Q28_data <- subset(Q28_data, Q28A!= 8)

line_data <- aggregate(Q28A~D4A, Q28_data,mean)
line_data <- cbind(line_data,aggregate(Q28B~D4A, Q28_data,mean)[2])
line_data <- cbind(line_data,aggregate(Q28C~D4A, Q28_data,mean)[2])

store_line_data <- line_data %>% 
  mutate(Industry = as.factor(D4A)) %>% 
  dplyr::rename(`Current` = Q28A, `1 Year` = Q28B, `3 Years` = Q28C) %>% 
  pivot_longer(Current:`3 Years`, names_to = "time") %>% 
  mutate(time=as.factor(time)) %>% 
  mutate(time = fct_relevel(time, c("Current","1 Year","3 Years")))

merged <- inner_join(labels,store_line_data, by="Industry") %>% 
  dplyr::rename(industry=Industry, Industry=names)

data <- data %>% 
  dplyr::rename(Industry=D4A) %>%
  mutate(Industry=as.factor(Industry)) %>% 
  inner_join(labels,data, by="Industry") %>% 
  dplyr::rename(industry=Industry, Industry=names)

# industries
D4A_count <-  BDM_Final_Clean %>%
  as.tibble() %>% 
  count(D4A) %>% 
  mutate(Industry=as.factor(D4A)) %>% 
  inner_join(labels,D4A_count,by="Industry") %>% 
  dplyr::rename(Count=n) %>% 
  select(-D4A) %>% 
  dplyr::rename(industry=Industry, Industry=names)

# industries after Q28 Not Sure = 8 removed
D4A_count_clean <-  Q28_data %>%
  as.tibble() %>% 
    count(D4A) %>% 
  mutate(Industry=as.factor(D4A)) %>% 
  inner_join(labels,D4A_count_clean,by="Industry") %>% 
  rename(Count=n) %>% 
  select(-D4A) %>% 
  dplyr::rename(industry=Industry, Industry=names)
```

* The considirations:
  + `Not Sure` is removed from the survey, which was 38% of the original data. 
  + `Accommodation and Food Services` has a rapid growth rate; however, this category has the highest uncertainty when considering the `Not Sure` answer for future hiring. 
  + Most of the `Accommodation and Food Services` businesses have the number of employees less than 50. It is interesting to see how rapidly the sector wants to grow over the next three years. 
```{r Q28 line data, fig.width=10, fig.height=6, fig.align='center'}
library(gghighlight)
ggplotly( 
  merged %>% 
  ggplot(aes(x=time, y=value, color=Industry, group=Industry)) + 
  geom_point() +
  geom_line() +
  ggtitle("How many positions do you project having open in Delaware? - Averaged") +
  xlab("Time Frame") +
  ylab("Average Positions") +
  #gghighlight(max(value) > 5.5) +
  #scale_y_discrete(breaks=c("2","3","4","5","6"),labels=c( "2","3","4","5-9","10+")) +
  theme_classic() 
  )

```

```{r d4a before, include=FALSE}

ggplotly( 
D4A_count %>% 
ggplot( aes(x=Industry, y=Count)) +
  geom_bar(stat="identity",color="blue",fill="steelblue")+
  theme_bw() +
  ggtitle("Distribution Industries") +
  xlab("Industries") +
  ylab("Count") +
  theme(axis.text.x = element_text(angle = 45)) +
  #geom_text_repel(aes(label = Q17_count$Question, data = Q17_count,fontface ="plain", color = "black", size = 3)) +
  theme(plot.title = element_text(size = 12, face = "bold")) +
  theme(axis.title.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(size = 8)) +
  geom_line(aes(y =Count), size = 1.5, color="red", group = 1))
```

```{r d4a after,include=FALSE}
ggplotly( 
D4A_count_clean %>% 
ggplot( aes(x=Industry, y=Count)) +
  geom_bar(stat="identity",color="blue",fill="steelblue")+
  theme_bw() +
  ggtitle("Distribution Industries - after Q28 Not Sure = 8 removed") +
  xlab("Industries") +
  ylab("Count") +
  theme(axis.text.x = element_text(angle = 45)) +
  #geom_text_repel(aes(label = Q17_count$Question, data = Q17_count,fontface ="plain", color = "black", size = 3)) +
  theme(plot.title = element_text(size = 12, face = "bold")) +
  theme(axis.title.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(size = 8)) +
  geom_line(aes(y =Count), size = 1.5, color="red", group = 1)+
  coord_flip()
)

```

```{r Q28A bar graph, fig.width=8,fig.height=6, include=FALSE}
### How many positions do you currently have open in Delaware that you're actively trying to fill?
Position <- cut(data$Q28A, breaks = c(0, 1, 5, 6, 7,8), labels = c("None","1-4","5-9","10+","Not Sure"))

ggplotly(
  data %>% 
  ggplot(aes(x=Industry,fill=Position)) + 
  geom_bar() +
  scale_fill_brewer(palette="Set1") + 
  ggtitle("Positions Actively Trying to Fill - Currently") +
  xlab("Industries") + 
  ylab("Count") +
  guides(fill = guide_legend(title = "Position to fill")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45)) +
  #geom_text_repel(aes(label = Q17_count$Question, data = Q17_count,fontface ="plain", color = "black", size = 3)) +
  theme(plot.title = element_text(size = 12, face = "bold")) +
  theme(axis.title.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(size = 8))
)
```

```{r Q28B bar graph, fig.width=8, fig.height=6,include=FALSE}
### How many positions do you project having open in Delaware a year from now? 
Position <- cut(data$Q28B, breaks = c(0, 1, 5, 6, 7,8), labels = c("None","1-4","5-9","10+","Not Sure"))

ggplotly(
  data %>% 
  ggplot(aes(x=Industry,fill=Position)) + 
  geom_bar() +
  scale_fill_brewer(palette="Set1") + 
  ggtitle("Positions Actively Trying to Fill - a Year from Now") +
  xlab("Industries") + 
  ylab("Count") +
  guides(fill = guide_legend(title = "Position to fill")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45)) +
  #geom_text_repel(aes(label = Q17_count$Question, data = Q17_count,fontface ="plain", color = "black", size = 3)) +
  theme(plot.title = element_text(size = 12, face = "bold")) +
  theme(axis.title.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(size = 8)) 
)

```

```{r Q28C bar graph, fig.width=8, fig.height=6,include=FALSE}
### How many positions do you project having open in Delaware three years from now?
Position <- cut(data$Q28C, breaks = c(0, 1, 5, 6, 7,8), labels = c("None","1-4","5-9","10+","Not Sure"))

ggplotly(
  data %>% 
  ggplot(aes(x=Industry,fill=Position)) +
  geom_bar() +
  scale_fill_brewer(palette="Set1") + 
  ggtitle("Positions Actively Trying to Fill - Three Years from Now") +
  xlab("Industries") + 
  ylab("Count") +
  guides(fill = guide_legend(title = "Position to fill")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45)) +
  #geom_text_repel(aes(label = Q17_count$Question, data = Q17_count,fontface ="plain", color = "black", size = 3)) +
  theme(plot.title = element_text(size = 12, face = "bold")) +
  theme(axis.title.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(size = 8)) 
)
```
 
 
### Mission Critical Positions That will be Lost
```{r Q37-38 use Q37 to correlate Q38}
data <- BDM_Final_Clean %>% select("D4A","Q37","Q38")
Q37_38_data <- subset(data, Q37!= 8)
Q37_38_data <- subset(Q37_38_data, Q38!= 8)

line_data <- aggregate(Q37~D4A, Q37_38_data,mean)
line_data <- cbind(line_data,aggregate(Q38~D4A, Q37_38_data,mean)[2])

store_line_data <- line_data %>% 
  mutate(Industry = as.factor(D4A)) %>% 
  dplyr::rename(`Next year` = Q37, `Next five years` = Q38) %>% 
  pivot_longer(`Next year`:`Next five years`, names_to = "Time") %>% 
  mutate(Time=as.factor(Time)) %>% 
  mutate(Time = fct_relevel(Time, c("Next year","Next five years")))

merged <- inner_join(labels,store_line_data, by="Industry") %>% 
  dplyr::rename(industry=Industry, Industry=names)

# industries
D4A_count <-  data %>%
  as.tibble() %>% 
  count(D4A) %>% 
  mutate(Industry=as.factor(D4A)) %>% 
  inner_join(labels,D4A_count,by="Industry") %>% 
  dplyr::rename(Count=n) %>% 
  select(-D4A) %>% 
  dplyr::rename(industry=Industry, Industry=names)

# industries after Q28 Not Sure = 8 removed
D4A_count_clean <-  Q37_38_data %>%
  as.tibble() %>% 
    count(D4A) %>% 
  mutate(Industry=as.factor(D4A)) %>% 
  inner_join(labels,D4A_count_clean,by="Industry") %>% 
  rename(Count=n) %>% 
  select(-D4A) %>% 
  dplyr::rename(industry=Industry, Industry=names)
```

```{r Q37-38 ggplotly, include=FALSE}

ggplotly( 
  merged %>% 
  ggplot(aes(x=Time, y=value, color=Industry, group=Industry)) + 
  geom_point() +
  geom_line() +
  ggtitle("How many mission critical positions will be lost due to retirement - Averaged") +
  xlab("Time Frame") +
  ylab("Average Positions") +
  #gghighlight(max(value) > 5.5) +
  #scale_y_discrete(breaks=c("2","3","4","5","6"),labels=c( "2","3","4","5-9","10+")) +
  theme_classic() 
  )
```

How many mission critical positions will be lost due to retirement?

```{r Q37-38 plotly, fig.width=10, fig.height=6, fig.align='center'}
fig <- plot_ly(
  data = merged,
  x = ~Time,
  y = ~value,
  color = ~Industry,
  type = "scatter",
  mode = "lines+markers",
  text = ~Industry,
  hovertemplate = ~paste(
    '</br><b> %{text}</b><br>',
    '</br> <b>Count:</b>',value
    )
  ) 
fig <- fig %>% 
  layout(title = list(text = '<b> </b>'),
         xaxis = list(title = list(text='<b> Time Frame</b>'), tickangle = 0,tickmode = "linear",range=c(-0.1,1.1)),
         #yaxis = list(range=c(1,6.)),
         yaxis = list(tickvals = c(1,2,3,4,5,6,7),ticktext = c("1","2","3","4","5-9","10+","")),
         yaxis = list(title = list(text='<b> Number of Positions </b>')),
         legend = list(title = list(text = '<b> Growth Industries </b>'))
         ) 
fig
```












## What Tools Do Employers Use When Recruiting? {.tabset}

### Frequency of Use 
```{r Q13-top-bottom data prepare}
library(plyr)
df <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q13_1 = length(D4A[Q13_1 == 1]), Q13_2 = length(D4A[Q13_2 == 1]), 
        Q13_3 = length(D4A[Q13_3 == 1]), Q13_4 = length(D4A[Q13_4 == 1]), 
        Q13_5 = length(D4A[Q13_5 == 1]), Q13_6 = length(D4A[Q13_6 == 1]), 
        Q13_7 = length(D4A[Q13_7 == 1]), Q13_8 = length(D4A[Q13_8 == 1]), 
        Q13_9 = length(D4A[Q13_9 == 1]), Q13_10 = length(D4A[Q13_10 == 1]), 
        Q13_11 = length(D4A[Q13_11 == 1]), Q13_12 = length(D4A[Q13_12 == 1]), 
        Q13_13 = length(D4A[Q13_13 == 1]), Q13_14 = length(D4A[Q13_14 == 1]), 
        Q13_15 = length(D4A[Q13_15 == 1]), Q13_16 = length(D4A[Q13_16 == 1]), 
        Q13_17 = length(D4A[Q13_17 == 1]))
detach("package:plyr", unload = TRUE)

library(dplyr)
Q13_count <- df %>%
  dplyr::rename(Industry=D4A) %>% 
  dplyr::mutate(Industry=as.factor(Industry)) %>% 
  inner_join(labels,Q13_count, by="Industry")


Q13_sum <-  Q13_count %>%
  dplyr::select(Q13_1:Q13_17) %>% 
  dplyr::summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  dplyr::rename(count = V1) %>% 
  dplyr::arrange(desc(count)) %>% 
  dplyr::mutate(Percentage = percent(round(count/sum(count),3))) %>% 
  dplyr::slice(c(1:5,13:17))%>% 
  dplyr::mutate(labels = paste0(Percentage," (",count,")")) %>% 
  dplyr::mutate(Tools = c(rep("Top 5",5),rep("Bottom 5",5)))

Q13_sum_top <- Q13_sum %>% 
  slice(1:5)

Q13_sum_bottom <- Q13_sum %>% 
  slice(6:10)

Q13_sum <- tibble::rownames_to_column(Q13_sum,"Variable")
Q13_sum <- inner_join(variable_info,Q13_sum, by="Variable")
Q13_sum_top <- tibble::rownames_to_column(Q13_sum_top,"Variable")
Q13_sum_top <- inner_join(variable_info,Q13_sum_top, by="Variable")
Q13_sum_bottom <- tibble::rownames_to_column(Q13_sum_bottom,"Variable")
Q13_sum_bottom <- inner_join(variable_info,Q13_sum_bottom, by="Variable")

# Q13 grouped ##################################################################
#Q13_1,Q13_2,Q13_3,Q13_4,Q13_5,Q13_6,Q13_7,Q13_8,Q13_9,Q13_10,Q13_11,Q13_12,Q13_13,Q13_14,Q13_15,Q13_16,Q13_17
# `Third-party recruiter/head-hunter/staffing firm`="Q13_1",
#          `Company website`="Q13_2",
#          `Delaware JobLink`="Q13_3",
#          `Jobvite`="Q13_4",
#          `Monster`="Q13_5",
#          `Indeed`="Q13_6",
#          `LinkedIn`="Q13_7",
#          `ZipRecruiter`="Q13_8",
#          `Glassdoor`="Q13_9",
#          `Social Media`="Q13_10",
#          `Facebook`="Q13_11",
#          `Twitter`="Q13_12",
#          `Instagram`="Q13_13",
#          `Word of mouth`="Q13_14",
#          `Direct campus recruiting/college fairs`="Q13_15",
#          `Career fairs`="Q13_16",
#          `Other`="Q13_17"
# Q13_count_all_ind <- Q13_count %>% 
#   tidyr::spread(Q13,Count) %>%
#   rename(
#   ) %>% 
#   replace(is.na(.), 0) %>% 
#   mutate(Industry = as.factor(Industry))


Q13_top5_all_ind <- Q13_count[, (names(Q13_count) %in% c("Industry","names",Q13_sum$Variable))]
#Q21 top non-technical skill across all industries
Q13_top5_all_ind <- Q13_top5_all_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Q13_2:Q13_17, names_to = "Variable") %>% 
  mutate(Variable=as.factor(Variable)) %>% 
  inner_join(variable_info,Q13_top5_all_ind, by = "Variable") %>% 
  rename(Count=value)
  # group_by(Question) %>% 
  # mutate(Percentage = round(100*Count/sum(Count),2)) %>% 
  # ungroup()


# wide format to long format
Q13_top5_all_ind1 <- Q13_top5_all_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  mutate(Question=as.factor(Question)) %>% 
  rename(industry=Industry, Answer=Question) %>% 
  rename(Industry=names)

# get the percentage data within answer and industry as well as total answer within industry
Q13_top5_all_ind1 <- Q13_top5_all_ind1 %>% 
  group_by(Industry) %>% 
  mutate(Percentage=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()

Q13_top5_all_ind1 <- Q13_top5_all_ind1 %>%
  group_by(Industry, Answer) %>% 
  summarise(Total = sum(Count)) %>% 
  ungroup() %>% 
  group_by(Industry) %>% 
  mutate(Percentage = round(Total/sum(Total),3)) %>%  
  ungroup() %>% 
  mutate(Industry = fct_reorder(Industry, Percentage))
```

```{r Q13, fig.width=10, fig.height=6, fig.align='center'}
Q13_sum[9,2] = "Word of mouth"
Q13_sum$Tools <- factor(Q13_sum$Tools,levels = c("Top 5", "Bottom 5"))

ggplotly(
  Q13_sum %>% 
ggplot(aes(x= reorder(Question,-count),
           y=count,
           text=paste(
             "<br><b> &#8226; Tool: </b>",Question,
             "<br><b> &#8226; Count: </b>",count,
             "<br><b> &#8226; Percentage among all tools: </b>",Percentage), 
           group=1, fill=Tools)) +
  geom_bar( stat = "identity") +
  labs(fill = "") +
  ggtitle("What Tools Do Employers Use? ") +
  xlab("Recruiting Tools") +
  ylab("Response of the Business (Count)") +
  theme(axis.text.x = element_text(size = 8)) +
  #guides(fill=guide_legend(title="Tools")) +
  theme_classic(),tooltip = c("text")
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
)
```

```{r Q13-top-pie, fig.height=5, fig.width=8, include=FALSE}
ggplot(Q13_sum_top,aes(x= "",y=count, fill=reorder(Question,-count))) +
  geom_bar(width = 1, stat = "identity", color="white", alpha=0.8) +
  coord_polar("y",start = 0) +
  ggtitle("Top-5: What Tools Do Employers Use?") +
  geom_text(aes(label = labels),position = position_stack(vjust = 0.5), size=3, color = "black") +
  guides(fill=guide_legend(title="Tools")) +
  theme_void() 
```

```{r Q13-bottom-pie, fig.width=5, fig.height=9, include=FALSE}
ggplot(Q13_sum_bottom,aes(x= "",y=count, fill=reorder(Question,-count))) +
  geom_bar(width = 1, stat = "identity", color="white", alpha=0.8) +
  coord_polar("y",start = 0) +
  ggtitle("Bottom-5: What Tools Do Employers Use?")+
  geom_text(aes(label = labels),position = position_stack(vjust = 0.5), size=3, color = "black") +
  guides(fill=guide_legend(title="Tools")) +
  theme_void() 
  #scale_fill_brewer(palette="Set3")
```


### Recruitment Tool Success Rate  
* It looks like the businesses using the highest vote for those tools they are actively using. 
  + `Social Media` has more approval ratings than `Facebook` (even though it is used more actively).   
```{r Q14-top-bottom data prepare}
library(plyr)
df1 <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q14A = length(D4A[Q14A == 1]), Q14B = length(D4A[Q14B == 1]), 
        Q14C = length(D4A[Q14C == 1]), Q14D = length(D4A[Q14D == 1]), 
        Q14E = length(D4A[Q14E == 1]), Q14F = length(D4A[Q14F == 1]), 
        Q14G = length(D4A[Q14G == 1]), Q14H = length(D4A[Q14H == 1]), 
        Q14I = length(D4A[Q14I == 1]), Q14J = length(D4A[Q14J == 1]), 
        Q14K = length(D4A[Q14K == 1]), Q14L = length(D4A[Q14L == 1]), 
        Q14M = length(D4A[Q14M == 1]), Q14N = length(D4A[Q14N == 1]), 
        Q14O = length(D4A[Q14O == 1]), Q14P = length(D4A[Q14P == 1]))

df2 <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q14A = length(D4A[Q14A == 2]), Q14B = length(D4A[Q14B == 2]), 
        Q14C = length(D4A[Q14C == 2]), Q14D = length(D4A[Q14D == 2]), 
        Q14E = length(D4A[Q14E == 2]), Q14F = length(D4A[Q14F == 2]), 
        Q14G = length(D4A[Q14G == 2]), Q14H = length(D4A[Q14H == 2]), 
        Q14I = length(D4A[Q14I == 2]), Q14J = length(D4A[Q14J == 2]), 
        Q14K = length(D4A[Q14K == 2]), Q14L = length(D4A[Q14L == 2]), 
        Q14M = length(D4A[Q14M == 2]), Q14N = length(D4A[Q14N == 2]), 
        Q14O = length(D4A[Q14O == 2]), Q14P = length(D4A[Q14P == 2]))
detach("package:plyr", unload = TRUE)
```

```{r Q14 data prep-2}
# D4A = df1["D4A"]
Q14_count <- bind_rows(df1, df2) %>% 
  group_by(D4A) %>% 
  summarise_all(sum) %>% 
  rename(Industry=D4A) %>% 
  mutate(Industry=as.factor(Industry)) %>% 
  ungroup()

Q14_count <- inner_join(labels,Q14_count, by="Industry")

Q14_sum <-  Q14_count %>%
  select(Q14A:Q14P) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(count = V1) %>% 
  arrange(desc(count)) %>% 
  mutate(Percentage = percent(round(count/sum(count),3))) %>% 
  slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",count,")"))

Q14_sum <- tibble::rownames_to_column(Q14_sum,"Variable")
Q14_sum <- inner_join(variable_info,Q14_sum, by="Variable")

Q14_sum[,2] = c("Company website", "Indeed","LinkedIn","Social Media","Word of mouth")
```

```{r Q14 plot, fig.width=8, fig.height=6, fig.align='center'}
#Q13_sum$Tools <- factor(Q13_sum$Tools,levels = c("Top 5", "Bottom 5"))

ggplotly(
  Q14_sum %>% 
ggplot(aes(x= reorder(Question,-count),
           y=count,
           text=paste(
             "<br><b> &#8226; Tool: </b>",Question,
             "<br><b> &#8226; Count: </b>",count,
             "<br><b> &#8226; Percent: </b>",Percentage), 
           group=1)) +
  geom_bar( stat = "identity",color="#2c7fb8",fill="#7fcdbb") +
  labs(fill = "") +
  ggtitle("Top 5 Successful Recruiting Tools that the Company Use Actively") +
  xlab("Recruiting Tools") +
  ylab("Response of the Business (Count)") +
  theme(axis.text.x = element_text(size = 8)) +
  #guides(fill=guide_legend(title="Tools")) +
  theme_classic(),tooltip = c("text")
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
)
```

```{r  Q14 pie chart, include=FALSE}
library(ggplot2)
ggplot(Q14_sum,aes(x= "",y=count, fill=Question)) +
  geom_bar(width = 1, stat = "identity", color="white", alpha=0.8) +
  coord_polar("y",start = 0) +
  ggtitle("Top-5 Services Recommended for Delaware JobLink") +
  geom_text(aes(label = labels),position = position_stack(vjust = 0.5), size=4.2, color = "white") +
  theme_void() + 
  scale_fill_brewer(palette="Set1")+
  guides(fill=guide_legend(title="Services"))
```











## Delaware JobLink {.tabset}

### Which Services Could the Delaware JobLink Provide That Would Help Your Business?
```{r Q16 Within Job Link, what are the top five tools cited - organize the data}
# Which services could the Delaware JobLink (Delaware JobLink provides job seekers, 
# employers, and training providers with easy-to-use tools that support a wide 
# range of activities) provide that would help your business (select all that apply)?

library(plyr)
df <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q16_1 = length(D4A[Q16_1 == 1]), Q16_2 = length(D4A[Q16_2 == 1]), 
        Q16_3 = length(D4A[Q16_3 == 1]), Q16_4 = length(D4A[Q16_4 == 1]), 
        Q16_5 = length(D4A[Q16_5 == 1]), Q16_6 = length(D4A[Q16_6 == 1]), 
        Q16_7 = length(D4A[Q16_7 == 1]), Q16_8 = length(D4A[Q16_8 == 1]), 
        Q16_9 = length(D4A[Q16_9 == 1]), Q16_10 = length(D4A[Q16_10 == 1]), 
        Q16_11 = length(D4A[Q16_11 == 1]), Q16_12 = length(D4A[Q16_12 == 1]), 
        Q16_13 = length(D4A[Q16_13 == 1]))
detach("package:plyr", unload = TRUE)
# require(plyr); detach(package:plyr) # to avoid conflict with dplyr

Q16_count <- df %>%
  rename(Industry=D4A) %>% 
  mutate(Industry=as.factor(Industry))

Q16_count <- inner_join(labels,Q16_count, by="Industry")
# Q16_sum <- data.frame(as.list(mapply(sum,Q16_count[,c(-1,-2,-3)])))

Q16_sum <-  Q16_count %>%
  select(Q16_1:Q16_13) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(count = V1) %>% 
  arrange(desc(count)) %>% 
  mutate(Percentage = percent(round(count/sum(count),3))) %>% 
  slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",count,")"))

Q16_sum <- tibble::rownames_to_column(Q16_sum,"Variable")
Q16_sum <- inner_join(variable_info,Q16_sum, by="Variable")

```

```{r Q16 pie chart, fig.width=10, fig.height=6, fig.align='center'}
# ggplotly(
#   Q16_sum %>% 
# ggplot(aes(x= reorder(Question,-count),
#           y=count,
#         text=paste(
#           "<br><b> &#8226; Tool: </b>",Question,
#          "<br><b>&#8226; Count: </b>",count,
#          "<br><b> &#8226; Percent: </b>",Percentage
#        ), group=1)) +
#   #theme(axis.text.x = element_text(angle = 90)) +
#   geom_bar( stat = "identity", position = "stack",color="blue",fill="steelblue") +
#   ggtitle("Which services could the Delaware JobLink provide that would help your business? - Top-5") +
#   xlab("Top-5 Services Recommended for Delaware JobLink") +
#   ylab("Response of the Business (Count)") +
#   theme(axis.text.x = element_text(angle = 90)) +
#   #geom_text_repel(aes(label = Q17_count$Question, data = Q17_count,fontface ="plain", color = "black", size = 3)) +
#   #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
#   theme_bw(),tooltip = c("text") 
# )

ggplot(Q16_sum,aes(x= "",y=count, fill=reorder(Question,-count))) +
  geom_bar(width = 1, stat = "identity", color="white", alpha=0.8) +
  coord_polar("y",start = 0) +
  ggtitle("Top-5 Services Recommended for Delaware JobLink") +
  geom_text(aes(label = labels),position = position_stack(vjust = 0.5), size=4.2, color = "white") +
  theme_void() + 
  scale_fill_brewer(palette="Set1")+
  guides(fill=guide_legend(title="Services"))
```


### Do You Use Delaware JobLink?
```{r Q30 look at distribution across industry- data prepare, fig.width=9}
data <- BDM_Final_Clean %>% select("SAM_NO","D4A","Q30") %>% rename(Industry=D4A)


# Q30 all industries ###########################################################
Q30_count_all_ind <- data %>% count(Industry,Q30, name = "Count")

# make it wide format
Q30_count_all_ind <- Q30_count_all_ind %>% 
  tidyr::spread(Q30,Count) %>%
  rename(Yes="1", No="2", `Not Sure`="3") %>% 
  replace(is.na(.), 0) %>% 
  mutate(Industry = as.factor(Industry))

# make it wide format
Q30_count_all_ind1 <- inner_join(labels,Q30_count_all_ind, by="Industry") 
Q30_count_all_ind1 <- Q30_count_all_ind1 %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(`Yes`:`Not Sure`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(industry=Industry, Count=value) %>% 
  rename(Industry=names)

# get the percentage data within answer and industry as well as total answer within industry
Q30_count_all_ind1 <- Q30_count_all_ind1 %>% 
  group_by(Industry) %>% 
  mutate(Percentage=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()


# Q30 sum ######################################################################
Q30_sum <-  Q30_count_all_ind %>%
  select(Yes:`Not Sure`) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(Count = V1) %>% 
  arrange(desc(Count)) %>% 
  mutate(Percentage = percent(round(Count/sum(Count),3))) %>% 
  #slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",Count,")"))
Q30_sum <- tibble::rownames_to_column(Q30_sum,"Variable")


# Q30 Growth industries ########################################################
# extract the growth industries
Q30_count_growth_ind  <- Q30_count_all_ind[Q30_count_all_ind$Industry %in%  
                                     c("1","3","4","7","9","10","12","13","15","16","18"),] 
Q30_count_growth_ind <- Q30_count_growth_ind %>% select(-Industry) # remove the first column
# group the growth industries
Q30_count_growth_ind <- cbind("Industry"= c(1,3,4,4,10,10,12,10,15,16,1),Q30_count_growth_ind)

# sum those industries in the same growth industry
Q30_count_growth_ind <- aggregate(. ~Industry, Q30_count_growth_ind, sum)
Q30_count_growth_ind <- inner_join(growth_industries, Q30_count_growth_ind, by = "Industry")
# wide format to long format
Q30_count_growth_ind <- Q30_count_growth_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Yes:`Not Sure`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(`Growth Industry`=names, Count=value)

# get the percentage data within answer and industry as well as total answer within industry
Q30_count_growth_ind <- Q30_count_growth_ind %>% 
  group_by(`Growth Industry`) %>% 
  mutate(Percent=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()
```

```{r Q30 all industries plot - ggplotly, fig.width=10, fig.height=6, fig.align='center'}
Q30_count_all_ind1$Answer <- factor(Q30_count_all_ind1$Answer,levels = c("Yes", "No", "Not Sure"))

ggplotly(
  Q30_count_all_ind1 %>%
    mutate(Percent_yes = if_else(Answer=="Yes",Percentage,NA_real_)) %>%
    fill(Percent_yes) %>%
    mutate(Industry=fct_reorder(Industry, Percent_yes)) %>% 
    ggplot(aes(x= Percentage,
               y=Industry,
               fill=Answer,
               text=paste(
                 "<b>&#8226; Growth industry: </b>",Industry,
                 "<br><b> &#8226; Count: </b>",Count,
                 "<br><b> &#8226; Response within industry %: </b>",Percentage*100),
               group=Industry
    )) +
    geom_col( position = "stack") +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_brewer(palette = "Set2") + 
    labs(title = "Percent of Delaware JobLink Use by Industry", 
         x = "Answer (Percentage)" , 
         y = "") +
    theme_classic() +
    theme(axis.text.x = element_text(angle  = 0,
                                     size = 8),
          plot.title = element_text(size = 11, 
                                    face = "bold"),
          axis.title.y = element_text(size = 11)),
  tooltip = c("text")
)
# flip coordinate
# 
```














## Assesing Hiring Requirements {.tabset}

### How Often Do You Assess the Minimum Hiring Requirements 
```{r Q12 look at distribution across industry, fig.width=10, fig.height=6}
#How often do you assess your job descriptions and minimum hiring requirements (i.e. requiring a high school diploma or a college degree)?

library(dplyr)
data <- BDM_Final_Clean %>% select("D4A","Q12") %>% rename(Industry=D4A)


# Q12 all industries ###########################################################
Q12_count_all_ind <- data %>% count(Industry,Q12, name = "Count")

# make it wide format
Q12_count_all_ind <- Q12_count_all_ind %>% 
  tidyr::spread(Q12,Count) %>%
  rename(`As the need arises`="1", `Every 1-2 months`="2", 
         `Every 3-6 months`="3", `Every 7-11 months`="4", 
         `Annually`="5",`Every 1-3 years`="6",`Every 4 years or longer`="7") %>% 
  replace(is.na(.), 0) %>% 
  mutate(Industry = as.factor(Industry))

# wide format to long format
Q12_count_all_ind1 <- inner_join(labels, Q12_count_all_ind, by = "Industry")

Q12_count_all_ind1 <- Q12_count_all_ind1 %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(`As the need arises`:`Every 4 years or longer`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(industry=Industry, Count=value) %>% 
  rename(Industry=names)

# get the percentage data within answer and industry as well as total answer within industry
Q12_count_all_ind1 <- Q12_count_all_ind1 %>% 
  group_by(Industry) %>% 
  mutate(Percentage=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()

Q12_count_all_ind1 <- Q12_count_all_ind1 %>%
  mutate(groupings = case_when(
    Answer %in% c("As the need arises") ~ "As the need arises",
    Answer %in% c("Every 1-2 months","Every 3-6 months") ~ "Every 1-6 months",
    Answer %in% c("Every 7-11 months", "Annually") ~ "Every 7 months -1 year",
    Answer %in% c("Every 1-3 years","Every 4 years or longer") ~ "Greater than annually")
  ) %>%
  group_by(Industry, groupings) %>% 
  summarise(Total = sum(Count)) %>% 
  ungroup() %>% 
  group_by(Industry) %>% 
  mutate(Percentage = round(Total/sum(Total),3)) %>%  
  ungroup() %>% 
  mutate(Industry = fct_reorder(Industry, Percentage))

# Q12 sum ######################################################################
Q12_sum <-  Q12_count_all_ind %>%
  select(`As the need arises`:`Every 4 years or longer`) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(Count = V1) %>% 
  arrange(desc(Count)) %>% 
  mutate(Percentage = percent(round(Count/sum(Count),3))) %>% 
  #slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",Count,")"))
Q12_sum <- tibble::rownames_to_column(Q12_sum,"Variable")


# Q12 Growth industries ########################################################
# extract the growth industries
Q12_count_growth_ind  <- Q12_count_all_ind[Q12_count_all_ind$Industry %in%  
                                     c("1","3","4","7","9","10","12","13","15","16","18"),] 
Q12_count_growth_ind <- Q12_count_growth_ind %>% select(-Industry) # remove the first column
# group the growth industries
Q12_count_growth_ind <- cbind("Industry"= c(1,3,4,4,10,10,12,10,15,16,1),Q12_count_growth_ind)

# sum those industries in the same growth industry
Q12_count_growth_ind <- aggregate(. ~ Industry, Q12_count_growth_ind, sum)
Q12_count_growth_ind <- inner_join(growth_industries, Q12_count_growth_ind, by = "Industry")

# wide format to long format
Q12_count_growth_ind <- Q12_count_growth_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(`As the need arises`:`Every 4 years or longer`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(`Growth Industry`=names, Count=value)

# get the percentage data within answer and industry as well as total answer within industry
Q12_count_growth_ind <- Q12_count_growth_ind %>% 
  group_by(`Growth Industry`) %>% 
  mutate(Percentage=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()


Q12_count_growth_ind$Answer <- factor(Q12_count_growth_ind$Answer,
                             levels=c("As the need arises", "Every 1-2 months",
                                      "Every 3-6 months", "Every 7-11 months",
                                      "Annually", "Every 1-3 years", "Every 4 years or longer"))

```

```{r Q12 growth industries - plotly, include=FALSE}
plot_ly(
  data = Q12_count_growth_ind,
  x = ~Answer,
  y = ~Count,
  color = ~`Growth Industry`,
  type = "bar",
  text = ~`Growth Industry`,
  hovertemplate = ~paste(
    '</br><b> %{text}</b><br>',
    '</br> <b>Count:</b>',Count,
    '</br> <b>Within company:</b>',Percentage
  )
) %>% 
  layout(barmode = "stack")
```

```{r Q12 ggplotly, fig.width=10, fig.height=6, fig.align='center'}

ggplotly(
  Q12_count_all_ind1 %>%
    mutate(Percent_yes = if_else(groupings=="As the need arises",Percentage,NA_real_)) %>%
    fill(Percent_yes) %>%
    mutate(Industry=fct_reorder(Industry, Percent_yes)) %>% 
    ggplot(aes(x= Percentage,
               y=Industry,
               fill=groupings,
               text=paste(
                 "<b>&#8226; Growth industry: </b>",Industry,
                 "<br><b> &#8226; Response within industry: </b>",100*Percentage,"%",
                 "<br><b> &#x2022; Total within industry: </b>",Total),
               group=Industry
    )) +
    geom_col( position = "stack") +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_brewer(palette = "Set2") + 
    labs(title = "Frequency of Assesing Job Description Across Industries", 
         x = "Frequency (Percentage)" , 
         y = "") +
    guides(fill = guide_legend(title = "Frequency")) +
    theme_classic() +
    theme(axis.text.x = element_text(angle  = 0, size = 8),
          plot.title = element_text(size = 11, face = "bold"),
          axis.title.y = element_text(size = 11)),
  tooltip = c("text")
)

```


### Do You Have Positions does not Require a College Degree?
```{r Q34 look at distribution across industry- data prepare, fig.width=9}
data <- BDM_Final_Clean %>% select("SAM_NO","D4A","Q34") %>% rename(Industry=D4A)


# Q34 all industries ###########################################################
Q34_count_all_ind <- data %>% count(Industry,Q34, name = "Count")

# make it wide format
Q34_count_all_ind <- Q34_count_all_ind %>% 
  tidyr::spread(Q34,Count) %>%
  rename(Yes="1", No="2", `Not Sure`="3") %>% 
  replace(is.na(.), 0) %>% 
  mutate(Industry = as.factor(Industry))

# make it wide format
Q34_count_all_ind1 <- inner_join(labels,Q34_count_all_ind, by="Industry") 
Q34_count_all_ind1 <- Q34_count_all_ind1 %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(`Yes`:`Not Sure`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(industry=Industry, Count=value) %>% 
  rename(Industry=names)

# get the percentage data within answer and industry as well as total answer within industry
Q34_count_all_ind1 <- Q34_count_all_ind1 %>% 
  group_by(Industry) %>% 
  mutate(Percentage=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()




# Q34 sum ######################################################################
Q34_sum <-  Q34_count_all_ind %>%
  select(Yes:`Not Sure`) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(Count = V1) %>% 
  arrange(desc(Count)) %>% 
  mutate(Percentage = percent(round(Count/sum(Count),3))) %>% 
  #slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",Count,")"))
Q34_sum <- tibble::rownames_to_column(Q34_sum,"Variable")


# Q34 Growth industries ########################################################
# extract the growth industries
Q34_count_growth_ind  <- Q34_count_all_ind[Q34_count_all_ind$Industry %in%  
                                     c("1","3","4","7","9","10","12","13","15","16","18"),] 
Q34_count_growth_ind <- Q34_count_growth_ind %>% select(-Industry) # remove the first column
# group the growth industries
Q34_count_growth_ind <- cbind("Industry"= c(1,3,4,4,10,10,12,10,15,16,1),Q34_count_growth_ind)

# sum those industries in the same growth industry
Q34_count_growth_ind <- aggregate(. ~Industry, Q34_count_growth_ind, sum)
Q34_count_growth_ind <- inner_join(growth_industries, Q34_count_growth_ind, by = "Industry")
# wide format to long format
Q34_count_growth_ind <- Q34_count_growth_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Yes:`Not Sure`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(`Growth Industry`=names, Count=value)

# get the percentage data within answer and industry as well as total answer within industry
Q34_count_growth_ind <- Q34_count_growth_ind %>% 
  group_by(`Growth Industry`) %>% 
  mutate(Percent=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()

#Q34_count_growth_ind$Answer <- factor(Q34_count_growth_ind$Answer,levels=c("Yes","No","Not Sure"))
```

```{r Q34 all industries plot - ggplotly, fig.width=10, fig.height=6, fig.align='center'}
Q34_count_all_ind1$Answer <- factor(Q34_count_all_ind1$Answer,levels = c("Yes", "No", "Not Sure"))

ggplotly(
  Q34_count_all_ind1 %>%
    mutate(Percent_yes = if_else(Answer=="Yes",Percentage,NA_real_)) %>%
    fill(Percent_yes) %>%
    mutate(Industry=fct_reorder(Industry, Percent_yes)) %>% 
    ggplot(aes(x= Percentage,
               y=Industry,
               fill=Answer,
               text=paste(
                 "<b> &#8226; Growth industry: </b>",Industry,
                 "<br><b> &#8226; Answer: </b>",Answer,
                 "<br><b> &#8226; Count: </b>",Count,
                 "<br><b> &#8226; Response within industry %: </b>",Percentage*100),
               group=Industry
    )) +
    geom_col( position = "stack") +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_brewer(palette = "Set2") + 
    labs(title = "Do You Have Positions does not Require a College Degree?", 
         x = "Answer (Percentage)" , 
         y = "") +
    theme_classic() +
    theme(axis.text.x = element_text(angle  = 0,
                                     size = 8),
          plot.title = element_text(size = 11, 
                                    face = "bold"),
          axis.title.y = element_text(size = 11)),
  tooltip = c("text")
) %>% layout(hoverlabel = list(align = "left")) 

```


### Individuals Coming out of the Criminal Justice System
Do You Accept Individuals Coming out of the Criminal Justice System by Industry?
```{r Q35 look at distribution across industry,, fig.width=8, include=FALSE}
### Do You Accept Individuals Coming out of the Criminal Justice System by Industry?
library(dplyr)
data <- BDM_Final_Clean %>% select("SAM_NO","D4A","Q35") %>% rename(Industry=D4A)


# Q35 all industries ###########################################################
Q35_count_all_ind <- data %>% count(Industry,Q35, name = "Count")
# make it wide format
Q35_count_all_ind <- Q35_count_all_ind %>% 
  tidyr::spread(Q35,Count) %>%
  rename(Yes="1", No="2", `Not Sure`="3") %>% 
  replace(is.na(.), 0) %>% 
  mutate(Industry = as.factor(Industry))
#Q35_count_all_ind <- inner_join(labels,Q35_count_all_ind, by="Industry") 


# make it wide format
Q35_count_all_ind1 <- inner_join(labels,Q35_count_all_ind, by="Industry") 
Q35_count_all_ind1 <- Q35_count_all_ind1 %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(`Yes`:`Not Sure`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(industry=Industry, Count=value) %>% 
  rename(Industry=names)

# get the percentage data within answer and industry as well as total answer within industry
Q35_count_all_ind1 <- Q35_count_all_ind1 %>% 
  group_by(Industry) %>% 
  mutate(Percentage=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()


# Q35 sum ######################################################################
Q35_sum <-  Q35_count_all_ind %>%
  select(Yes:`Not Sure`) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(Count = V1) %>% 
  arrange(desc(Count)) %>% 
  mutate(Percentage = percent(round(Count/sum(Count),3))) %>% 
  #slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",Count,")"))
Q35_sum <- tibble::rownames_to_column(Q35_sum,"Variable")


# Q35 Growth industries ########################################################
# extract the growth industries
Q35_count_growth_ind  <- Q35_count_all_ind[Q35_count_all_ind$Industry %in%  
                                     c("1","3","4","7","9","10","12","13","15","16","18"),] 
Q35_count_growth_ind <- Q35_count_growth_ind %>% select(-Industry) # remove the first column
# group the growth industries
Q35_count_growth_ind <- cbind("Industry"= c(1,3,4,4,10,10,12,10,15,16,1),Q35_count_growth_ind)

# sum those industries in the same growth industry
Q35_count_growth_ind <- aggregate(. ~ Industry, Q35_count_growth_ind, sum)
Q35_count_growth_ind <- inner_join(growth_industries, Q35_count_growth_ind, by = "Industry")
# wide format to long format
Q35_count_growth_ind <- Q35_count_growth_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Yes:`Not Sure`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(`Growth Industry`=names, Count=value)

# get the percentage data within answer and industry as well as total answer within industry
Q35_count_growth_ind <- Q35_count_growth_ind %>% 
  group_by(`Growth Industry`) %>% 
  mutate(Percent=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()
```

```{r Q35 ggplotly, fig.width=10, fig.height=6, fig.align='center'}

Q35_count_all_ind1$Answer <- factor(Q35_count_all_ind1$Answer,levels = c("Yes", "No", "Not Sure"))

ggplotly(
  Q35_count_all_ind1 %>% 
    mutate(Percent_yes = if_else(Answer=="Yes",Percentage,NA_real_)) %>%
    fill(Percent_yes) %>%
    mutate(Industry=fct_reorder(Industry, Percent_yes)) %>% 
    ggplot(aes(x= Percentage,
               y=Industry,
               fill=Answer,
               text=paste(
                 "<b> &#8226; Growth industry: </b>",Industry,
                 "<br><b> &#8226; Answer: </b>",Answer,
                 "<br><b> &#8226; Count: </b>",Count,
                 "<br><b> &#8226; Response within industry %: </b>",Percentage*100),
               group=Industry
    )) +
    geom_col( position = "stack") +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_brewer(palette = "Set2") + 
    labs(title = "Individuals Coming out of the Criminal Justice System by Industry", 
         x = "Answer (Percentage)" , 
         y = "") +
    theme_classic() +
    theme(axis.text.x = element_text(angle  = 0,
                                     size = 8),
          plot.title = element_text(size = 11, 
                                    face = "bold"),
          axis.title.y = element_text(size = 11)),
  tooltip = c("text")
) %>% layout(hoverlabel = list(align = "left")) 

```












## Applicant Qualification (Training) {.tabset}

### Applicants Education Level
```{r Q17 Distribution of the Answers: Level1:Very Important and Level2: Somewhat Important)}
target_industries <- c("Financial & Business Services","Healthcare","Education",
              "Manufacturing, Logistics and Transportation","Food & Agriculture",
              "Science & Technology","Construction & Mechanical Trades ")
# [D4A==c(1,3,4,7,10,12,15,16,18)]
Q17_labels <- paste("Q17",LETTERS[1:13],sep="")
Q17_tr_label <- data.frame("Q17_list" = c(1:13),
                           "Variable" = Q17_labels,
                           "training"=c("High schools",
                                        "Career and Technical Education programs",
                                        "Libraries",
                                        "Delaware 2-year public colleges",
                                        "Delaware 4-year public colleges",
                                        "Delaware 4-year Private colleges",
                                        "Out of state 2-year public colleges",
                                        "Out of state 4-year public colleges",
                                        "Out of state 4-year Private colleges",
                                        "Labor unions",
                                        "Local workforce development board(s)",
                                        "Non-profit/private training providers",
                                        "Apprenticeships")
                           )

#industries with answer level1
library(plyr)
df1 <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q17A = length(D4A[Q17A == 1]), Q17B = length(D4A[Q17B == 1]), 
        Q17C = length(D4A[Q17C == 1]), Q17D = length(D4A[Q17D == 1]), 
        Q17E = length(D4A[Q17E == 1]), Q17F = length(D4A[Q17F == 1]), 
        Q17G = length(D4A[Q17G == 1]), Q17H = length(D4A[Q17H == 1]), 
        Q17I = length(D4A[Q17I == 1]), Q17J = length(D4A[Q17J == 1]), 
        Q17K = length(D4A[Q17K == 1]), Q17L = length(D4A[Q17L == 1]), 
        Q17M = length(D4A[Q17M == 1]))
#industries with answer level2
df2 <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q17A = length(D4A[Q17A == 2]), Q17B = length(D4A[Q17B == 2]), 
        Q17C = length(D4A[Q17C == 2]), Q17D = length(D4A[Q17D == 2]), 
        Q17E = length(D4A[Q17E == 2]), Q17F = length(D4A[Q17F == 2]), 
        Q17G = length(D4A[Q17G == 2]), Q17H = length(D4A[Q17H == 2]),
        Q17I = length(D4A[Q17H == 2]), Q17J = length(D4A[Q17J == 2]), 
        Q17K = length(D4A[Q17K == 2]), Q17L = length(D4A[Q17L == 2]), 
        Q17M = length(D4A[Q17M == 2]))
detach("package:plyr", unload = TRUE)
# require(plyr); detach(package:plyr) # to avoid conflict with dplyr

#remove non target industries
# df2 <- df2 %>% slice(-c(4,5,7,8,10,12,13,16,18,19)) %>%
#   rename(Industry=D4A) %>%
#   mutate(Industry=as.factor(Industry))
# df2 <- inner_join(labels,df2, by="Industry")
# 
# #remove non target industries
# df_1 <- df1[df1$D4A %in% c("1","3","4","7","9","10","12","13","15","16","18"),] %>% 
#   rename(Industry=D4A) %>% 
#   mutate(Industry=as.factor(Industry))
# df_1 <- inner_join(labels,df_1, by="Industry")
```

```{r Q17 Get the count per industry, message=FALSE}
# library(tidyverse)
library(ggplot2)
# Q17_count <- read_csv("Q17_count2.csv")
# Q17_info <- variable_info$Question[127:139]
# Q17_count <- Q17_count %>% add_column(Q17_value=Q17_info, .after="Question")
# write.csv(Q17_count,"/Users/yuksel/OneDrive/Documents/Tech_Impact/DWDB_BI/Q17_count2.csv")

# Q17 all industries ###########################################################
Q17_count_all_ind <- bind_rows(df1, df2) %>% 
  group_by(D4A) %>% 
  summarise_all(sum) %>% 
  rename(Industry=D4A) %>% 
  mutate(Industry=as.factor(Industry)) %>% 
  ungroup()

# wide format to long format
Q17_count_all_ind1 <- inner_join(labels, Q17_count_all_ind, by = "Industry")

Q17_count_all_ind1 <- Q17_count_all_ind1 %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Q17A:Q17M, names_to = "Variable") %>%  
  mutate(Variable=as.factor(Variable)) %>% 
  rename(industry=Industry, Count=value) %>% 
  rename(Industry=names) %>% 
  inner_join(Q17_tr_label,Q17_count_growth_ind, by = "Variable") %>% 
  rename(Answer=training)


# Q17_count_growth_ind <- Q17_count_growth_ind %>% 
#   mutate(Industry = as.factor(Industry)) %>% 
#   pivot_longer(Q17A:Q17M, names_to = "Variable") %>% 
#   mutate(Variable=as.factor(Variable)) %>% 
#   inner_join(Q17_tr_label,Q17_count_growth_ind, by = "Variable")


# get the percentage data within answer and industry as well as total answer within industry
Q17_count_all_ind1 <- Q17_count_all_ind1 %>% 
  group_by(Industry) %>% 
  mutate(Percentage=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()


Q17_count_all_ind1 <- Q17_count_all_ind1 %>%
  mutate(groupings = case_when(
    Answer %in% c("High schools") ~ "High schools",
    Answer %in% c("Apprenticeships") ~ "Apprenticeships",
    Answer %in% c("Delaware 2-year public colleges", "Out of state 2-year public colleges") ~ "2-year colleges",
    Answer %in% c("Delaware 4-year public colleges",
                  "Delaware 4-year Private colleges",
                  "Out of state 4-year public colleges",
                  "Out of state 4-year Private colleges") ~ "4-year colleges",
    Answer %in% c("Career and Technical Education programs",
                  "Libraries",
                  "Labor unions",
                  "Local workforce development board(s)",
                  "Non-profit/private training providers") ~ "2-year colleges")
  ) %>%
  group_by(Industry, groupings) %>% 
  summarise(Total = sum(Count)) %>% 
  ungroup() %>% 
  group_by(Industry) %>% 
  mutate(Percentage = round(Total/sum(Total),3)) %>%  
  ungroup() %>% 
  mutate(Industry = fct_reorder(Industry, Percentage))


# Q17 sum ######################################################################
Q17_sum <-  Q17_count_all_ind %>%
  select(Q17A:Q17M) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(Count = V1) %>% 
  arrange(desc(Count)) %>% 
  mutate(Percentage = percent(round(Count/sum(Count),3))) %>% 
  #slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",Count,")"))

Q17_sum <- tibble::rownames_to_column(Q17_sum,"Variable")
Q17_sum <- inner_join(Q17_tr_label,Q17_sum, by="Variable")


# Q17 growth industries ########################################################
# extract the growth industries
Q17_count_growth_ind  <- Q17_count_all_ind[Q17_count_all_ind$Industry %in%  
                          c("1","3","4","7","9","10","12","13","15","16","18"),]
Q17_count_growth_ind <- Q17_count_growth_ind %>% select(-Industry) # remove the first column
Q17_count_growth_ind <- cbind("Industry"= c(1,3,4,4,10,10,12,10,15,16,1),Q17_count_growth_ind)
  
Q17_count_growth_ind <- aggregate(. ~ Industry, Q17_count_growth_ind, sum)
Q17_count_growth_ind <- inner_join(growth_industries, Q17_count_growth_ind, by = "Industry")

Q17_count_growth_ind <- Q17_count_growth_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Q17A:Q17M, names_to = "Variable") %>% 
  mutate(Variable=as.factor(Variable)) %>% 
  inner_join(Q17_tr_label,Q17_count_growth_ind, by = "Variable")

```

```{r Q17-a,fig1, fig.height = 5, fig.width = 7, include=FALSE}
ggplotly( 
Q17_sum %>% 
ggplot( aes(x=training, y=Count)) +
  geom_bar(stat="identity",color="blue",fill="steelblue")+
  theme_bw() +
  ggtitle("Distribution of Very and Somewhat Important Responses by Bussiness") +
  xlab("Applicants Education Level (Training)") +
  ylab("Very/Somewhat Important Responses (Count)") +
  theme(axis.text.x = element_text(angle = 90)) +
  #geom_text_repel(aes(label = Q17_count$Question, data = Q17_count,fontface ="plain", color = "black", size = 3)) +
  theme(plot.title = element_text(size = 12, face = "bold")) +
  theme(axis.title.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(size = 8)) +
  scale_x_discrete(labels= Q17_tr_label$training))
```

```{r Q17 ggplotly, fig.width=10, fig.height=6, fig.align='center'}

ggplotly(
  Q17_count_all_ind1 %>%
    mutate(Percent_yes = if_else(groupings=="2-year colleges",Percentage,NA_real_)) %>%
    fill(Percent_yes) %>%
    mutate(Industry=fct_reorder(Industry, Percent_yes)) %>% 
    ggplot(aes(x= Percentage,
               y=Industry,
               fill=groupings,
               text=paste(
                 "<b>&#8226; Growth industry: </b>",Industry,
                 "<br><b> &#8226; Response within industry: </b>",100*Percentage,"%",
                 "<br><b> &#x2022; Total within industry: </b>",Total),
               group=Industry
    )) +
    geom_col( position = "stack") +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_brewer(palette = "Set2") + 
    labs(title = "Distribution of Very and Somewhat Important Responses by Bussiness", 
         x = "Applicants Education Level (Percentage)" , 
         y = "") +
    guides(fill = guide_legend(title = "Applicants Education Level")) +
    theme_classic() +
    theme(axis.text.x = element_text(angle  = 0, size = 8),
          plot.title = element_text(size = 11, face = "bold"),
          axis.title.y = element_text(size = 11)),
  tooltip = c("text")
)

```


###  Are New Applicants in Meeting the Skills and Qualifications?
How ready are new applicants in meeting the skills and qualifications for the job they are applying for?
```{r Q36 look at distribution across industry}
###  How ready are new applicants in meeting the skills and qualifications for the job they are applying for?
library(dplyr)
data <- BDM_Final_Clean %>% select("SAM_NO","D4A","Q36") %>% rename(Industry=D4A)


# Q36 all industries ###########################################################
Q36_count_all_ind <- data %>% count(Industry,Q36, name = "Count")

# make it wide format
Q36_count_all_ind <- Q36_count_all_ind %>% 
  tidyr::spread(Q36,Count) %>%
  rename(`Very ready`="1", `Somewhat ready`="2", `Not very ready`="3", `Not at all ready`="4", `Not sure`="5") %>% 
  replace(is.na(.), 0) %>% 
  mutate(Industry = as.factor(Industry))

# wide format to long format
Q36_count_all_ind1 <- inner_join(labels, Q36_count_all_ind, by = "Industry")
Q36_count_all_ind1 <- Q36_count_all_ind1 %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(`Very ready`:`Not sure`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(industry=Industry, Count=value) %>% 
  rename(Industry=names)

# get the percentage data within answer and industry as well as total answer within industry
Q36_count_all_ind1 <- Q36_count_all_ind1 %>% 
  group_by(Industry) %>% 
  mutate(Percentage=round(Count/sum(Count),3), Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()
# Q36_count_all_ind1 <- Q36_count_all_ind1 %>%
#   group_by(Industry, groupings) %>% 
#   summarise(Total = sum(Count)) %>% 
#   ungroup() %>% 
#   group_by(Industry) %>% 
#   mutate(Percentage = round(Total/sum(Total),3)) %>%  
#   ungroup() %>% 
#   mutate(Industry = fct_reorder(Industry, Percentage))

# Q36 sum ######################################################################
Q36_sum <-  Q36_count_all_ind %>%
  select(`Very ready`:`Not sure`) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(Count = V1) %>% 
  arrange(desc(Count)) %>% 
  mutate(Percentage = percent(round(Count/sum(Count),3))) %>% 
  #slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",Count,")"))
Q36_sum <- tibble::rownames_to_column(Q36_sum,"Variable")


# Q36 Growth industries ########################################################
# extract the growth industries
Q36_count_growth_ind  <- Q36_count_all_ind[Q36_count_all_ind$Industry %in%  
                                     c("1","3","4","7","9","10","12","13","15","16","18"),] 
Q36_count_growth_ind <- Q36_count_growth_ind %>% select(-Industry) # remove the first column
# group the growth industries
Q36_count_growth_ind <- cbind("Industry"= c(1,3,4,4,10,10,12,10,15,16,1),Q36_count_growth_ind)

# sum those industries in the same growth industry
Q36_count_growth_ind <- aggregate(. ~ Industry, Q36_count_growth_ind, sum)
Q36_count_growth_ind <- inner_join(growth_industries, Q36_count_growth_ind, by = "Industry")

# wide format to long format
Q36_count_growth_ind <- Q36_count_growth_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(`Very ready`:`Not sure`, names_to = "Answer") %>% 
  mutate(Answer=as.factor(Answer)) %>% 
  rename(`Growth Industry`=names, Count=value)

# get the percentage data within answer and industry as well as total answer within industry
Q36_count_growth_ind <- Q36_count_growth_ind %>% 
  group_by(`Growth Industry`) %>% 
  mutate(Percent=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()

Q36_count_growth_ind$Answer <- factor(Q36_count_growth_ind$Answer,
                             levels=c("Very ready", "Somewhat ready", "Not very ready", "Not at all ready", "Not sure"))
```

```{r Q36 ggplotly, fig.width=10, fig.height=6, fig.align='center'}
Q36_count_all_ind1$Answer <- factor(Q36_count_all_ind1$Answer,
                             levels=c("Very ready", "Somewhat ready", "Not very ready", "Not at all ready", "Not sure"))

ggplotly(
  Q36_count_all_ind1 %>%
    mutate(Percent_yes = if_else(Answer=="Very ready",Percentage,NA_real_)) %>%
    fill(Percent_yes) %>%
    mutate(Industry=fct_reorder(Industry, Percent_yes)) %>% 
    ggplot(aes(x= Percentage,
               y=Industry,
               fill=Answer,
               text=paste(
                 "<b>&#8226; Growth industry: </b>",Industry,
                 "<br><b> &#8226; Answer: </b>",Answer,
                 "<br><b> &#8226; Response within industry: </b>",100*Percentage,"%",
                 "<br><b> &#x2022; Total within industry: </b>",Total),
               group=Industry
    )) +
    geom_col( position = "stack") +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_brewer(palette = "Set2") + 
    labs(title = "How ready are new applicants?", 
         x = "Answer (Percentage)" , 
         y = "") +
    guides(fill = guide_legend(title = "Answer")) +
    theme_classic() +
    theme(axis.text.x = element_text(angle  = 0, size = 8),
          plot.title = element_text(size = 11, face = "bold"),
          axis.title.y = element_text(size = 11)),
  tooltip = c("text")
)
```

```{r Q36 plotly, fig.width=10, fig.height=6, fig.align='center', include=FALSE}
fig <- plot_ly(
  data = Q36_count_all_ind1,
  x = ~reorder(Answer,-Total),
  y = ~Count,
  color = ~Industry,
  type = "bar",
  text = ~Industry,
  hovertemplate = ~paste(
    '</br><b> %{text}</b><br>',
    '</br> <b>Count:</b>',Count,
    '</br> <b>Within Answer:</b>',Percentage
  )
) 

fig <- fig %>% 
  layout(barmode = "stack",
         title = list(text = '<b> How ready are new applicants?</b>'),
         xaxis = list(title = list(text='<b> </b>')),
         #xaxis = list(title = list(text='<b> Responses</b>'), tickangle = 0,tickmode = "linear",range=c(-0.1,1.1)),
         #yaxis = list(range=c(0,6)),
         #yaxis = list(tickvals = c(1,2,3,4,5,6),ticktext = c("1","2","3","4","5-9","10+")),
         yaxis = list(title = list(text='<b> Response of the Business (Count) </b>')),
         legend = list(title = list(text = '<b> Industries</b>'))
         #xaxis = list(categoryorder = "total descending")
  )
fig

```


### Non-Technical Skills
Which of the following non-technical skills do you find commonly lacking among job applicants or new employees?
```{r Q21}
library(plyr)
df <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q21_1 = length(D4A[Q21_1 == 1]), Q21_2 = length(D4A[Q21_2 == 1]), 
        Q21_3 = length(D4A[Q21_3 == 1]), Q21_4 = length(D4A[Q21_4 == 1]), 
        Q21_5 = length(D4A[Q21_5 == 1]), Q21_6 = length(D4A[Q21_6 == 1]), 
        Q21_7 = length(D4A[Q21_7 == 1]), Q21_8 = length(D4A[Q21_8 == 1]), 
        Q21_9 = length(D4A[Q21_9 == 1]), Q21_10 = length(D4A[Q21_10 == 1]), 
        Q21_11 = length(D4A[Q21_11 == 1]), Q21_12 = length(D4A[Q21_12 == 1]), 
        Q21_13 = length(D4A[Q21_13 == 1]), Q21_14 = length(D4A[Q21_14 == 1]), 
        Q21_15 = length(D4A[Q21_15 == 1]), Q21_16 = length(D4A[Q21_16 == 1]), 
        Q21_17 = length(D4A[Q21_17 == 1]), Q21_18 = length(D4A[Q21_18 == 1]), 
        Q21_19 = length(D4A[Q21_19 == 1]))
detach("package:plyr", unload = TRUE)
# require(plyr); detach(package:plyr) # to avoid conflict with dplyr

Q21_count <- df %>%
  rename(Industry=D4A) %>% 
  mutate(Industry=as.factor(Industry))

Q21_count <- inner_join(labels,Q21_count, by="Industry")
# Q21_sum <- data.frame(as.list(mapply(sum,Q21_count[,c(-1,-2,-3)])))

Q21_sum <-  Q21_count %>%
  select(Q21_1:Q21_19) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(count = V1) %>% 
  arrange(desc(count)) %>% 
  mutate(Percentage = percent(round(count/sum(count),3))) %>% 
  slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",count,")"))

Q21_sum <- tibble::rownames_to_column(Q21_sum,"Variable")
Q21_sum <- inner_join(variable_info,Q21_sum, by="Variable")

Q21_top5_all_ind <- Q21_count[, (names(Q21_count) %in% c("Industry","names",Q21_sum$Variable))]

#Q21 top non-technical skill across all industries
Q21_top5_all_ind <- Q21_top5_all_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Q21_1:Q21_13, names_to = "Variable") %>% 
  mutate(Variable=as.factor(Variable)) %>% 
  inner_join(variable_info,Q21_top5_all_ind, by = "Variable") %>% 
  rename(Count=value)
  # group_by(Question) %>% 
  # mutate(Percentage = round(100*Count/sum(Count),2)) %>% 
  # ungroup()


# wide format to long format
Q21_top5_all_ind1 <- Q21_top5_all_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  mutate(Question=as.factor(Question)) %>% 
  rename(industry=Industry, Answer=Question) %>% 
  rename(Industry=names)

# get the percentage data within answer and industry as well as total answer within industry
Q21_top5_all_ind1 <- Q21_top5_all_ind1 %>% 
  group_by(Industry) %>% 
  mutate(Percentage=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()

Q21_top5_all_ind1 <- Q21_top5_all_ind1 %>%
  group_by(Industry, Answer) %>% 
  summarise(Total = sum(Count)) %>% 
  ungroup() %>% 
  group_by(Industry) %>% 
  mutate(Percentage = round(Total/sum(Total),3)) %>%  
  ungroup() %>% 
  mutate(Industry = fct_reorder(Industry, Percentage))
```

```{r Q21 ggplotly, fig.width=10, fig.height=6, fig.align='center', include=FALSE}
ggplotly(
  Q21_top5_all_ind1 %>%
    mutate(Percent_yes = if_else(Answer=="Attention to detail",Percentage,NA_real_)) %>%
    fill(Percent_yes) %>%
    mutate(Industry=fct_reorder(Industry, Percent_yes)) %>% 
    ggplot(aes(x= Percentage,
               y=Industry,
               fill=Answer,
               text=paste(
                 "<b> &#8226; Industry: </b>",Industry,
                 "<br><b> &#8226; Response within industry: </b>",100*Percentage,"%",
                 "<br><b> &#x2022; Total within industry: </b>",Total),
               group=Industry
    )) +
    geom_col( position = "stack") +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_brewer(palette = "Set2") + 
    labs(title = "Non-Technical skills Lacking among Job Applicants Across Industries", 
         x = "Non-Technical Skills (Percentage)" , 
         y = "") +
    guides(fill = guide_legend(title = "Frequency")) +
    theme_classic() +
    theme(axis.text.x = element_text(angle  = 0, size = 8),
          plot.title = element_text(size = 11, face = "bold"),
          axis.title.y = element_text(size = 11)),
  tooltip = c("text")
)
```

```{r Q21 plotly, fig.width=10, fig.height=6, fig.align='center'}
fig <- plot_ly(
  data = Q21_top5_all_ind1,
  x = ~reorder(Answer,-Total),
  y = ~Total,
  color = ~Industry,
  type = "bar",
  text = ~Industry,
  hovertemplate = ~paste(
    '</br><b> %{text}</b><br>',
    '</br> <b>Count:</b>',Total,
    '</br> <b>Within Answer:</b>',Percentage
  )
) 

fig <- fig %>% 
  layout(barmode = "stack",
         title = list(text = '<b> Non-Technical Skills Lacking among Job Applicants Across Industries</b>'),
         xaxis = list(title = list(text='<b> Non-Technical Skills</b>')),
         #xaxis = list(tickangle = 0,tickmode = "linear",range=c(-0.1,1.1)),
         #yaxis = list(range=c(0,6)),
         #yaxis = list(tickvals = c(1,2,3,4,5,6),ticktext = c("1","2","3","4","5-9","10+")),
         yaxis = list(title = list(text='<b> Response of the Business (Count) </b>')),
         legend = list(title = list(text = '<b> Industries</b>'))
         #xaxis = list(categoryorder = "total descending")
  )
fig
```

### Non-Technical Skills are Most Difficult to Recruit? 
Which of the following non-technical skills are most difficult to recruit for? 
```{r Q23A data prepare}
library(plyr)
df <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q23A_1 = length(D4A[Q23A_1 == 1]), Q23A_2 = length(D4A[Q23A_2 == 1]), 
        Q23A_3 = length(D4A[Q23A_3 == 1]), Q23A_4 = length(D4A[Q23A_4 == 1]), 
        Q23A_5 = length(D4A[Q23A_5 == 1]), Q23A_6 = length(D4A[Q23A_6 == 1]), 
        Q23A_7 = length(D4A[Q23A_7 == 1]), Q23A_8 = length(D4A[Q23A_8 == 1]), 
        Q23A_9 = length(D4A[Q23A_9 == 1]), Q23A_10 = length(D4A[Q23A_10 == 1]), 
        Q23A_11 = length(D4A[Q23A_11 == 1]), Q23A_12 = length(D4A[Q23A_12 == 1]), 
        Q23A_13 = length(D4A[Q23A_13 == 1]), Q23A_14 = length(D4A[Q23A_14 == 1]), 
        Q23A_15 = length(D4A[Q23A_15 == 1]), Q23A_16 = length(D4A[Q23A_16 == 1]), 
        Q23A_17 = length(D4A[Q23A_17 == 1]), Q23A_18 = length(D4A[Q23A_18 == 1]), 
        Q23A_19 = length(D4A[Q23A_19 == 1]))
detach("package:plyr", unload = TRUE)
# require(plyr); detach(package:plyr) # to avoid conflict with dplyr

Q23A_count <- df %>%
  rename(Industry=D4A) %>% 
  mutate(Industry=as.factor(Industry))

Q23A_count <- inner_join(labels,Q23A_count, by="Industry")
# Q23A_sum <- data.frame(as.list(mapply(sum,Q23A_count[,c(-1,-2,-3)])))

Q23A_sum <-  Q23A_count %>%
  select(Q23A_1:Q23A_19) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(count = V1) %>% 
  arrange(desc(count)) %>% 
  mutate(Percentage = percent(round(count/sum(count),3))) %>% 
  slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",count,")"))

Q23A_sum <- tibble::rownames_to_column(Q23A_sum,"Variable")
Q23A_sum <- inner_join(variable_info,Q23A_sum, by="Variable")

Q23A_top5_all_ind <- Q23A_count[, (names(Q23A_count) %in% c("Industry","names",Q23A_sum$Variable))]

#Q23A top non-technical skill across all industries
Q23A_top5_all_ind <- Q23A_top5_all_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Q23A_1:Q23A_14, names_to = "Variable") %>% 
  mutate(Variable=as.factor(Variable)) %>% 
  inner_join(variable_info,Q23A_top5_all_ind, by = "Variable") %>% 
  rename(Count=value) %>% 
  group_by(Question) %>% 
  mutate(Percent = round(100*Count/sum(Count),2)) %>% 
  ungroup()
```

```{r Q23A plotly, fig.width=10, fig.height=6, fig.align='center'}
fig <- plot_ly(
  data = Q23A_top5_all_ind,
  x = ~reorder(Question,-Count),
  y = ~Count,
  color = ~names,
  type = "bar",
  text = ~names,
  hovertemplate = ~paste(
    '</br><b> %{text}</b><br>',
    '</br> <b>Count:</b>',Count,
    '</br> <b>Within Answer:</b>',Percent
  )
) 

fig <- fig %>% 
  layout(barmode = "stack",
         title = list(text = '<b> Non-Technical Skills that Hard to Find </b>'),
         xaxis = list(title = list(text='<b> Non-Technical Skills</b>')),
         #xaxis = list(title = list(text='<b> Responses</b>'), tickangle = 0,tickmode = "linear",range=c(-0.1,1.1)),
         #yaxis = list(range=c(0,6)),
         #yaxis = list(tickvals = c(1,2,3,4,5,6),ticktext = c("1","2","3","4","5-9","10+")),
         yaxis = list(title = list(text='<b> Response of the Business (Count) </b>')),
         legend = list(title = list(text = '<b> Industries</b>'))
         #xaxis = list(categoryorder = "total descending")
  )
fig

```


### Technical/Digital Skills
Which of the following technical/digital skills do you find commonly lacking among job applicants or new employees? 
```{r Q22}
library(plyr)
df <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q22_1 = length(D4A[Q22_1 == 1]), Q22_2 = length(D4A[Q22_2 == 1]), 
        Q22_3 = length(D4A[Q22_3 == 1]), Q22_4 = length(D4A[Q22_4 == 1]), 
        Q22_5 = length(D4A[Q22_5 == 1]), Q22_6 = length(D4A[Q22_6 == 1]), 
        Q22_7 = length(D4A[Q22_7 == 1]), Q22_8 = length(D4A[Q22_8 == 1]), 
        Q22_9 = length(D4A[Q22_9 == 1]), Q22_10 = length(D4A[Q22_10 == 1]), 
        Q22_11 = length(D4A[Q22_11 == 1]), Q22_12 = length(D4A[Q22_12 == 1]), 
        Q22_13 = length(D4A[Q22_13 == 1]), Q22_14 = length(D4A[Q22_14 == 1]), 
        Q22_15 = length(D4A[Q22_15 == 1]), Q22_16 = length(D4A[Q22_16 == 1]), 
        Q22_17 = length(D4A[Q22_17 == 1]), Q22_18 = length(D4A[Q22_18 == 1]), 
        Q22_19 = length(D4A[Q22_19 == 1]), Q22_20 = length(D4A[Q22_20 == 1]), 
        Q22_21 = length(D4A[Q22_21 == 1]))
detach("package:plyr", unload = TRUE)
# require(plyr); detach(package:plyr) # to avoid conflict with dplyr

Q22_count <- df %>%
  rename(Industry=D4A) %>% 
  mutate(Industry=as.factor(Industry))

Q22_count <- inner_join(labels,Q22_count, by="Industry")
# Q22_sum <- data.frame(as.list(mapply(sum,Q22_count[,c(-1,-2,-3)])))

Q22_sum <-  Q22_count %>%
  select(Q22_1:Q22_21) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(count = V1) %>% 
  arrange(desc(count)) %>% 
  mutate(Percentage = percent(round(count/sum(count),3))) %>% 
  slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",count,")"))

Q22_sum <- tibble::rownames_to_column(Q22_sum,"Variable")
Q22_sum <- inner_join(variable_info,Q22_sum, by="Variable")

Q22_top5_all_ind <- Q22_count[, (names(Q22_count) %in% c("Industry","names",Q22_sum$Variable))]

#Q22 top non-technical skill across all industries
Q22_top5_all_ind <- Q22_top5_all_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Q22_1:Q22_21, names_to = "Variable") %>% 
  mutate(Variable=as.factor(Variable)) %>% 
  inner_join(variable_info,Q22_top5_all_ind, by = "Variable") %>% 
  rename(Count=value) %>% 
  group_by(Question) %>% 
  mutate(Percent = round(100*Count/sum(Count),2)) %>% 
  ungroup()

# wide format to long format
Q22_top5_all_ind1 <- Q22_top5_all_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  mutate(Question=as.factor(Question)) %>% 
  rename(industry=Industry, Answer=Question) %>% 
  rename(Industry=names)

# get the percentage data within answer and industry as well as total answer within industry
Q22_top5_all_ind1 <- Q22_top5_all_ind1 %>% 
  group_by(Industry) %>% 
  mutate(Percentage=round(Count/sum(Count),3), G_Total=sum(Count)) %>% 
  ungroup() %>% 
  group_by(Answer) %>% 
  mutate(Ans=round(Count/sum(Count),3)) %>% 
  ungroup()

Q22_top5_all_ind1 <- Q22_top5_all_ind1 %>%
  group_by(Industry, Answer) %>% 
  summarise(Total = sum(Count)) %>% 
  ungroup() %>% 
  group_by(Industry) %>% 
  mutate(Percentage = round(Total/sum(Total),3)) %>%  
  ungroup() %>% 
  mutate(Industry = fct_reorder(Industry, Percentage))


```

```{r Q22 plotly, fig.width=10, fig.height=6, fig.align='center'}
fig <- plot_ly(
  data = Q22_top5_all_ind,
  x = ~reorder(Question,-Count),
  y = ~Count,
  color = ~names,
  type = "bar",
  text = ~names,
  hovertemplate = ~paste(
    '</br><b> %{text}</b><br>',
    '</br> <b>Count:</b>',Count,
    '</br> <b>Within Answer:</b>',Percent
  )
) 

fig <- fig %>% 
  layout(barmode = "stack",
         title = list(text = '<b> Technical/Digital Skills Lacking among Job Applicants Across Industries</b>'),
         xaxis = list(title = list(text='<b> Technical/Digital Skills</b>')),
         #xaxis = list(title = list(text='<b> Responses</b>'), tickangle = 0,tickmode = "linear",range=c(-0.1,1.1)),
         #yaxis = list(range=c(0,6)),
         #yaxis = list(tickvals = c(1,2,3,4,5,6),ticktext = c("1","2","3","4","5-9","10+")),
         yaxis = list(title = list(text='<b> Response of the Business (Count) </b>')),
         legend = list(title = list(text = '<b> Industries</b>'))
         #xaxis = list(categoryorder = "total descending")
  )
fig
```

```{r Q22 ggplotly, fig.width=10, fig.height=6, fig.align='center', include=FALSE}
ggplotly(
  Q22_top5_all_ind1 %>%
    mutate(Percent_yes = if_else(Answer=="Basic computer use/computer literacy",Percentage,NA_real_)) %>%
    fill(Percent_yes) %>%
    mutate(Industry=fct_reorder(Industry, Percent_yes)) %>% 
    ggplot(aes(x= Percentage,
               y=Industry,
               fill=Answer,
               text=paste(
                 "<b>&#8226; Industry: </b>",Industry,
                 "<br><b> &#8226; Response within industry: </b>",100*Percentage,"%",
                 "<br><b> &#x2022; Total within industry: </b>",Total),
               group=Industry
    )) +
    geom_col( position = "stack") +
    scale_x_continuous(labels = scales::percent) +
    scale_fill_brewer(palette = "Set2") + 
    labs(title = "Technical/Digital skills Lacking among Job Applicants Across Industries", 
         x = "Technical/Digital Skills (Percentage)" , 
         y = "") +
    guides(fill = guide_legend(title = "Technical/Digital Skills")) +
    theme_classic() +
    theme(axis.text.x = element_text(angle  = 0, size = 8),
          plot.title = element_text(size = 11, face = "bold"),
          axis.title.y = element_text(size = 11)),
  tooltip = c("text")
)
```
Businesses in Delaware are looking for applicants that have self-motivation.

### Technical/Digital Skills are Most Difficult to Recruit?  
Which of the following technical/digital skills are most difficult to recruit for?  
```{r Q23B}
library(plyr)
df <- ddply(BDM_Final_Clean,.(D4A), summarize,  
        Q23B_1 = length(D4A[Q23B_1 == 1]), Q23B_2 = length(D4A[Q23B_2 == 1]), 
        Q23B_3 = length(D4A[Q23B_3 == 1]), Q23B_4 = length(D4A[Q23B_4 == 1]), 
        Q23B_5 = length(D4A[Q23B_5 == 1]), Q23B_6 = length(D4A[Q23B_6 == 1]), 
        Q23B_7 = length(D4A[Q23B_7 == 1]), Q23B_8 = length(D4A[Q23B_8 == 1]), 
        Q23B_9 = length(D4A[Q23B_9 == 1]), Q23B_10 = length(D4A[Q23B_10 == 1]), 
        Q23B_11 = length(D4A[Q23B_11 == 1]), Q23B_12 = length(D4A[Q23B_12 == 1]), 
        Q23B_13 = length(D4A[Q23B_13 == 1]), Q23B_14 = length(D4A[Q23B_14 == 1]), 
        Q23B_15 = length(D4A[Q23B_15 == 1]), Q23B_16 = length(D4A[Q23B_16 == 1]), 
        Q23B_17 = length(D4A[Q23B_17 == 1]), Q23B_18 = length(D4A[Q23B_18 == 1]), 
        Q23B_19 = length(D4A[Q23B_19 == 1]), Q23B_20 = length(D4A[Q23B_20 == 1]), 
        Q23B_21 = length(D4A[Q23B_21 == 1]))
detach("package:plyr", unload = TRUE)
# require(plyr); detach(package:plyr) # to avoid conflict with dplyr

Q23B_count <- df %>%
  rename(Industry=D4A) %>% 
  mutate(Industry=as.factor(Industry))

Q23B_count <- inner_join(labels,Q23B_count, by="Industry")
# Q23B_sum <- data.frame(as.list(mapply(sum,Q23B_count[,c(-1,-2,-3)])))

Q23B_sum <-  Q23B_count %>%
  select(Q23B_1:Q23B_21) %>% 
  summarise_all(.,.funs = sum) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(count = V1) %>% 
  arrange(desc(count)) %>% 
  mutate(Percentage = percent(round(count/sum(count),3))) %>% 
  slice(1:5)%>% 
  mutate(labels = paste0(Percentage," (",count,")"))

Q23B_sum <- tibble::rownames_to_column(Q23B_sum,"Variable")
Q23B_sum <- inner_join(variable_info,Q23B_sum, by="Variable")

Q23B_top5_all_ind <- Q23B_count[, (names(Q23B_count) %in% c("Industry","names",Q23B_sum$Variable))]

#Q23B top non-technical skill across all industries
Q23B_top5_all_ind <- Q23B_top5_all_ind %>% 
  mutate(Industry = as.factor(Industry)) %>% 
  pivot_longer(Q23B_4:Q23B_21, names_to = "Variable") %>% 
  mutate(Variable=as.factor(Variable)) %>% 
  inner_join(variable_info,Q23B_top5_all_ind, by = "Variable") %>% 
  rename(Count=value) %>% 
  group_by(Question) %>% 
  mutate(Percent = round(100*Count/sum(Count),2)) %>% 
  ungroup()
```

```{r Q23B plotly, fig.width=10, fig.height=6, fig.align='center'}
fig <- plot_ly(
  data = Q23B_top5_all_ind,
  x = ~reorder(Question,-Count),
  y = ~Count,
  color = ~names,
  type = "bar",
  text = ~names,
  hovertemplate = ~paste(
    '</br><b> %{text}</b><br>',
    '</br> <b>Count:</b>',Count,
    '</br> <b>Within Answer:</b>',Percent
  )
) 

fig <- fig %>% 
  layout(barmode = "stack",
         title = list(text = '<b> Technical/Digital Skills that Hard to Find </b>'),
         xaxis = list(title = list(text='<b> Technical/Digital Skills</b>')),
         #xaxis = list(title = list(text='<b> Responses</b>'), tickangle = 0,tickmode = "linear",range=c(-0.1,1.1)),
         #yaxis = list(range=c(0,6)),
         #yaxis = list(tickvals = c(1,2,3,4,5,6),ticktext = c("1","2","3","4","5-9","10+")),
         yaxis = list(title = list(text='<b> Response of the Business (Count) </b>')),
         legend = list(title = list(text = '<b> Industries</b>'))
         #xaxis = list(categoryorder = "total descending")
  )
fig
```







